Models of lens candidates from Space Warps CFHTLS

### 2017-02-19 parts/massmodel.tex
edits

Once a spaghetti diagram has been drawn on a web browser, it is
forwarded to a server-side numerical framework, which searches for
mass maps consistent with the given image locations, parities and time
ordering.  The mass maps are made up of mass tiles and are free-form,
but are required to be concentrated around the identified lens centre
\citep[see][for the precise formulation of the search
  problem.]{2014MNRAS.445.2181C} Assuming such mass distributions can
be found (in practise, usually the case) a statistical ensemble of
two-dimensional mass maps is returned.  This ensemble, along with
derived quantities and uncertainties, makes up one SpaghettiLens
model.

@@

Figure~\ref{fig:kappa} shows projected mass maps of the example
systems.  This figure shows the tiled character of the mass map.  (The
mass maps displayed during modelling interpolated over the tiles.)
The modelling numerics uses an analytical integral over square tiles,
so the lens equation is always continuous and the arrival time is
smooth.  We also remark that this figure refers to the ensemble
average of each model, and the spread in the ensemble is not shown
here; the arrival-time surfaces and synthetic images in the two
previous figures also derive from the ensemble-average mass
distribution.  Figure~\ref{fig:encl} shows the enclosed-mass profiles,
expressed as the average convergence $\kappa$ within circles of given
projected radius.  This time, uncertainties are included.
Appendix~\ref{subsec:hires} describes improvements made since our
earlier work \citep{2015MNRAS.447.2170K}, to allow for steeper
profiles in the inner regions.  The enclosed mass is typically best
constrained at the notional Einstein radius, becoming more uncertain
at larger and smaller radii.

>>>>

Once a spaghetti diagram has been drawn on a web browser, it is
forwarded to a server-side numerical framework, which searches for
mass maps consistent with the given image locations, parities and time
ordering.  The mass maps are made up of mass tiles and are free-form,
but are required to be concentrated around the identified lens centre
\citep[see][for the precise formulation of the search
  problem.]{2014MNRAS.445.2181C} Assuming such mass distributions can
be found (which in practise is usually the case) a statistical
ensemble of two-dimensional mass maps is returned.  This ensemble,
along with derived quantities and uncertainties, makes up one
SpaghettiLens model.

@@

Figure~\ref{fig:kappa} shows projected mass maps of the example
systems.  Actually, this figure only shows the ensemble-average mass
maps, and not the variation within the ensemble, from which
uncertainties can be inferred.  (The same applies to the arrival-time
surfaces and synthetic images in the two previous figures.
Uncertainties will be shown in a concise form later, with
Figure~\ref{fig:encl}.)  Figure~\ref{fig:kappa} makes evident the
tiled nature of the mass model.  The tiles can be smoothed over by
interpolating, and this was actually done in the mass maps shown
online during the modelling process.  It is interesting, however, to
see the tiling artifacts, if only as a reminder that the substructure
in the mass distribution are very uncertain, even if some integrated
quantities are very well constrained.  How the free-form mass maps
relate to parameterised lens models is discussed in
Appendix~\ref{subsec:parameter}.  Note that the arrival-time surface
does not have discontinuous jumps, because the modelling numerics uses
an analytical integral over square tiles; likewise the lens equation.

Figure~\ref{fig:encl} shows the enclosed-mass profiles,
expressed as the average convergence $\kappa$ within circles of given
projected radius.  This time, uncertainties are included.
Appendix~\ref{subsec:hires} describes improvements made since our
earlier work \citep{2015MNRAS.447.2170K}, to allow for steeper
profiles in the inner regions.  The enclosed mass is typically best
constrained at the notional Einstein radius, becoming more uncertain
at larger and smaller radii.
